Current State of Knowledge Representation Systems for Robotics

### 2011-11-23 krs-survey.tex
Added a 'Summary of Approaches' section, with hints to the future content
Also changed/added a few other minor sections

\subsubsection{Pyschological tests}
\label{sect|evaluation-tests}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Comparison criteria}
\label{sect|comparison-criteria}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{sect|conclusion}

\subsection{Main groups}

\subsection{What is not successfully covered by current systems}

\subsection{Future challenges}
\label{sect|future-challenges}

>>>>

\subsubsection{Benchmarking}
\label{sect|benchmarking}

\cite{Hawes2008}: benchmarking of "Information-Processing Architectures on Intelligent Systems"
\subsubsection{Pyschological tests}
\label{sect|evaluation-tests}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Compared features}
\label{sect|compared-features}

@@

\subsubsection{Agent-dependent models}
\label{sect|multiple-models}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary of Approaches}
\label{sect|summary}

This section tries to summary the various approaches we surveyed in the
previous section.  This summary does not exactly follow the list of compared
features presented in section~\ref{sect|compared-features}. We have organized
it along four axis: \emph{what can be represented?}, \emph{How knowledge is
created and grounded?}, \emph{What can be done with the knowledge?} and
\emph{How to use knowledge in the whole, larger robot architecture?}.

\subsection{Expressiveness: what can we represent in the current state-of-the-art?}
\label{sect|summary-expressiveness}

\begin{itemize}
	\item expressiveness
\end{itemize}

\subsection{Creating and grounding knowledge in the physical world}
\label{sect|summary-grounding}

\begin{itemize}
	\item which knowledge modalities can be merged
	\item which grounding strategies
\end{itemize}

\subsection{Exploiting knowledge}
\label{sect|summary-knowledge-sources-reasoning}

\begin{itemize}
	\item which common-sense knowledge is used
	\item what kind of reasoning is made
	\item introspection
\end{itemize}

\subsection{Using a knowledge representation system in a larger robotic cognitive architecture}
\label{sect|summary-integration}

\begin{itemize}
	\item a priori evaluation/lazy evaluation and trade-offs (relations to events, scalability, detection of inconsistencies,...)
	\item relation with planning (action representation, temporal representation...)
	\item API/bindings/integration into executive layers
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Towards the next generation of Knowledge Representation Systems for Robotics}
\label{sect|conclusion}

\subsection{Current shotcomings: what is not successfully covered by current systems}

\subsection{Towards a new design}
